Preregistration

### 2019-05-04 analysis/survey/preregistration.Rmd
Refine wording for transparency and accountability

- *Financial transparency*: Timely and reliable disclosure regarding donations and financial allocations. 
- *Accountability*: An obligation or willingness to accept responsibility or to account for one's actions.

>>>>

- *Financial transparency*: Organization discloses information regarding its donations and financial allocations in a timely and reliable manner.
- *Accountability*: Organization undergoes a regular third-party audit to ensure that it is meeting its program goals and obligations.
